### 2023-07-30 README.Rmd
re-build README

This repository contains the data and code for our paper:

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Bartholdy, B.P., Hasselstrøm, J.B., Sørensen, L.K., Casna, M., Hoogland, M., Historisch Genootschap Beemster, & Henry, A.G. (2023). _`r Title`_. Zenodo, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.7649151>

@@

Please cite this compendium as:

> Bartholdy, B.P., Hasselstrøm, J.B., Sørensen, L.K., Casna, M., Hoogland, M., Historisch Genootschap Beemster, & Henry, A.G., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.7649825>

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.pdf`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

@@

You can download the compendium as a zip from from this URL:
[main.zip](/archive/main.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.qmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console

>>>>

This repository contains the data and code for our paper:
<!--
> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:
-->
> Bartholdy, B.P., Hasselstrøm, J.B., Sørensen, L.K., Casna, M., Hoogland, M., Historisch Genootschap Beemster, & Henry, A.G. (2023). _`r Title`_. Zenodo, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.7649151>

@@

Use the above paper to cite this compendium.
<!--
Please cite this compendium as:

> Bartholdy, B.P., Hasselstrøm, J.B., Sørensen, L.K., Casna, M., Hoogland, M., Historisch Genootschap Beemster, & Henry, A.G., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.7649825>
-->

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.pdf`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/data/): Data output from `data-raw/*.R`, used in the analysis (*.rda*).
  - [:file\_folder: analysis/figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
  - [:file\_folder: R](/R/): R functions.
  - [:file\_folder: data-raw](/data-raw/): R script to download and process the
    raw data from Zenodo (https://zenodo.org/record/8061483).

@@

You can download the compendium as a zip from from this URL:
[main.zip](/archive/main.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.qmd` and knit to produce the PDF manuscript (`_output/`),
  or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console.
